Spatiotemporal Multi-Resolution Approximation of the Amari Type Neural Field Model

### 2012-02-03 Multiresolution_framework/ltx/manuscript.tex
edit to the em alg
minor edit

In summary, to solve the joint state and parameter estimation for linear state-space models one can adapt the EM algorithm, solving the smoothing problem for the E-step and constructing and maximizing the lower bound in the M-step. A schematic representation of the EM algorithm is represented in Figure~\ref{fig:EMBlockDiagram}.  

@@

 The rest of this section is to construct the lower bound $\mathcal Q$ for the linear state-space model given by \eqref{eq:StateEquation} and \eqref{eq:ReducedObservationEquation}. The joint probability distribution $p(\mathbf X,\mathbf Y;\boldsymbol \theta)$ can be written as

>>>>

In summary, to solve the joint state and parameter estimation for linear state-space models one can adapt the EM algorithm, solving the smoothing problem for the E-step and constructing and maximizing the lower bound in the M-step. A schematic representation of the EM algorithm is represented in Figure~\ref{fig:EMBlockDiagram}. Note the algorithm can be initialized by either a random parameter set or a sequence of the random bounded state vectors. Here the latter is chosen as shown in the block diagram ensuring the resultant kernel is stable.  

@@

 The rest of this section is dedicated to the construction of the lower bound, $\mathcal Q$, for the linear state-space model given by \eqref{eq:StateEquation} and \eqref{eq:ReducedObservationEquation}. The joint probability distribution $p(\mathbf X,\mathbf Y;\boldsymbol \theta)$ can be written as
